FATE summary results

### 2019-09-17 paper draft.Rmd
Added rolling correlations for all climate time series
End of the day!

@@

>>>>

# re-run with al climate TS, not just the ones meeting the loadings threshold used above

# set up res.df with all TS
   res.df <- data.frame(ID = rep(seq_len(n_ts),
                                 n_years),
                        Time = sort(rep(seq_len(n_years), n_ts)), 
                        mean = c(t(apply(pred, c(3, 4), mean))), 
                        lo = c(t(apply(pred, c(3, 4), quantile, 0.025))),
                        hi = c(t(apply(pred, c(3, 4), quantile, 0.975))), 
                        y = c(modelfit$data))

# look at rolling correlations between fitted and observed values, as in Ecology paper
# using 25-yr rolling windows!
 index <- unique(res.df$ID)
    dfa.cor <- data.frame()

ggplot(filter(dfa.cor, window==25), aes(year, mean.cor)) + 
  theme_bw() + theme(axis.title.x = element_blank()) +
  geom_line(color=cb[3]) + facet_wrap(~ID, 
        scales = "free_y", ncol=3) + xlab("Year") + ylab("Correlation")

ggsave("goa climate dfa correlations 25 year windows all TS.png", height = 5, width=6, units="in")    
```

@@

# as for climate data, recalculate rolling correlations with all time series
modelfit <- GOA.biol$best_model

modelfit <- GOA.biol$best_model

  index <- unique(res.df$ID)

# using 25-yr rolling windows!

# and plot 25-yr windows
ggplot(filter(dfa.cor, window==25), aes(year, mean.cor)) + 
  theme_bw() + theme(axis.title.x = element_blank()) +
  geom_line(color=cb[3]) + facet_wrap(~ID, 
        scales = "free_y", ncol=4) + xlab("Year") + ylab("Correlation")

ggsave("goa biology dfa correlations 25 year windows all time series.png", height = 6.5, width=8, units="in")
```
